Analysis of epistatic inflation under large single additive effects, with a focus on the replication rate

### 2020-01-31 null_replication/docs/analyse_results.rmd
upd

# chi(4) version of lambda
mean(res$lambda_disc2)
sd(res$lambda_disc2) / sqrt(nrow(res))
```

>>>>

# chi(4) version of lambda
mean(res$lambda_disc2)
sd(res$lambda_disc2) / sqrt(nrow(res))

group_by(res, cis, sentinel, i) %>%
summarise(m=mean(lambda_disc2), v=sd(lambda_disc2)) %>%
plot(m ~ v, .)

library(ggplot2)
ggplot(res, aes(y=lambda_disc2, x=paste(i, sentinel, cis))) +
geom_boxplot()
